\textbf{The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models}

### 2021-04-15 Manuscripts/Manuscript v5/Manuscript_AM_v4.Rmd
Created folder for v5 of the manuscript

---
title: '**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**'
subtitle: _Beyond repeated measures ANOVA and Linear Mixed Models_
author:
- Ariel Mundo^[Department of Biomedical Engineering, University of Arkansas, Fayetteville]
- Timothy J. Muldoon^[Department of Biomedical Engineering, University of Arkansas,
  Fayetteville]
- John R. Tipton^[Department of Mathematical Sciences, University of Arkansas, Fayetteville]
output:
  bookdown::pdf_document2:
    keep_tex: yes
    fig_caption: yes
    extra_dependencies:
      subfig: null
      breqn: null
      caption: ["font={small}"]
      float: null
  bookdown::html_document2: default
  bookdown::word_document2:
    fig_caption: yes
    keep_md: yes
  link-citations: yes
  css: style.css
  '': default
csl: Elsevier.csl
bibliography: refs.bib
---

@@

\begin{equation}
y_{ijt} = \beta_0+ \beta_1 \times time_{t} + \beta_2 \times treatment_{j} + \beta_3 \times time_{t}\times treatment_{j}+\varepsilon_{ijt}\\ 
(\#eq:linear-model)
\end{equation}

>>>>

---
title: '**The statistical analysis of non-linear longitudinal data in biomedical research using generalized additive models**'
subtitle: _Beyond repeated measures ANOVA and Linear Mixed Models_
author:
- Ariel Mundo^[Department of Biomedical Engineering, University of Arkansas, Fayetteville]
- Timothy J. Muldoon^[Department of Biomedical Engineering, University of Arkansas,
  Fayetteville]
- John R. Tipton^[Department of Mathematical Sciences, University of Arkansas, Fayetteville]
output:
  bookdown::pdf_document2:
    keep_tex: yes
    fig_caption: yes
    extra_dependencies:
      subfig: null
      breqn: null
      caption: ["font={small}"]
      float: null
  bookdown::word_document2:
    fig_caption: yes
    keep_md: yes
  bookdown::html_document2: default
  link-citations: yes
  css: style.css
  '': default
csl: elsevier-with-titles.csl
bibliography: refs.bib
---

@@

\begin{equation}
y_{ijt} = \beta_0+\beta_1 \times time_{t} +\beta_2 \times treatment_{j} +\beta_3 \times time_{t}\times treatment_{j}+\varepsilon_{ijt}\\ 
(\#eq:linear-model)
\end{equation}

### 2021-04-15 Manuscripts/Manuscript v5/Manuscript_AM_v4.tex
Created folder for v5 of the manuscript

\begin{equation}
y_{ijt} = \beta_0+\beta_1 \times time_{t} +\beta_2 \times \textrm{treatment}_{j} +\beta_3 \times time_{t}\times \textrm{treatment}_{j}+\varepsilon_{ijt}\\ 
\label{eq:linear-model}
\end{equation}

@@

\begin{equation}
y_{ijt} = \beta_0+ \beta_1 \times time_{t} + \beta_2 \times \textrm{treatment}_{j} + \beta_3 \times time_{t}\times \textrm{treatment}_{j}+\mu_{ij} +\varepsilon_{ijt}\\ 
\label{eq:LMEM}
\end{equation}

>>>>

\begin{equation}
y_{ijt} = \beta_0+\beta_1 \times time_{t} +\beta_2 \times treatment_{j} +\beta_3 \times time_{t}\times treatment_{j}+\varepsilon_{ijt}\\ 
\label{eq:linear-model}
\end{equation}

@@

\begin{equation}
y_{ijt} = \beta_0+ \beta_1 \times time_{t} + \beta_2 \times treatment_{j} + \beta_3 \times time_{t}\times treatment_{j}+\mu_{ij} +\varepsilon_{ijt}\\ 
\label{eq:LMEM}
\end{equation}
